---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


## Load Library
```{r, message=FALSE, warning=FALSE}
library(C50)
library(tidyverse)
library(tidymodels)
library(janitor)
library(skimr)
library(kableExtra)
library(GGally)
library(kableExtra)
library(vip)
library(fastshap)
library(MASS)
library(rpart.plot)
library(factoextra)
library(imputeMissings)
library(ISLR)
library(tree)
```


## Import Data
```{r}
mkt <- read_csv("marketing_campaign.csv") %>% clean_names()
new <- read_csv("new_customers_mkt.csv") %>% clean_names()

mkt = subset(mkt, select = -c(z_cost, z_rev))
```


## Exploratory Analysis
```{r}
mkt_summary <- mkt %>%
  count(response) %>%
  mutate(pct = n/sum(n))

mkt_summary %>%
  ggplot(aes(x = factor(response), y = pct)) +
  geom_col() +
  geom_text(aes(label = round(pct, 2)), vjust = 2.5, color = "white") +
  labs(title = "Customers' Repsonse to Last Marketing Campaign", x = "Response", y = "Pct")

mkt %>%
  mutate(age = 2022 - birth) %>%
  ggplot(aes(x = age, fill = factor(response))) +
  geom_bar() +
  labs(title = "Response by Age")

mkt %>%
  mutate(mar_stat = as.factor(mar_stat)) %>%
  ggplot(aes(x = mar_stat, fill = factor(response))) +
  geom_bar() +
  labs(title = "Response by Marriage Status")

ggplot(mkt, aes(x = kids, fill = factor(response))) +
  geom_bar() +
  labs(title = "Response by Kids at Home")

mkt %>%
  mutate(education = as.factor(education)) %>%
  ggplot(aes(x = education, fill = factor(response))) +
  geom_bar() +
  labs(title = "Response by Education Level")
```


## Prepara Data for Clustering
```{r}
mkt <- mkt %>%
  mutate(age = 2022 - birth)

# -- impute numeric with median
mkt1 <- mkt %>% imputeMissings::impute()

# -- scale the numeric data
mkt1$age <- scale(mkt1$age)
mkt1$income <- scale(mkt1$income)
mkt1$kids <- scale(mkt1$kids)
mkt1$wines <- scale(mkt$wines)
mkt1$fruits <- scale(mkt$fruits)
mkt1$meat <- scale(mkt$meat)
mkt1$fish <- scale(mkt$fish)
mkt1$sweets <- scale(mkt$sweets)
mkt1$gold <- scale(mkt$gold)
mkt1$web <- scale(mkt$web)
mkt1$deals <- scale(mkt1$deals)
mkt1$web <- scale(mkt1$web)
mkt1$catalog <- scale(mkt1$catalog)
mkt1$store <- scale(mkt1$store)

mkt1 = subset(mkt1, select = -c(id, dt_customer, mar_stat, birth, education, response, teens, recency, visits))

skim(mkt1)
```


## Visually Choose Number of Clusters
```{r}
fviz_nbclust(mkt1, kmeans, method = "wss")
```


## Generate & Visualize Clusters
```{r}
set.seed(904)

cluster <- kmeans(mkt1, 7, iter.max = 200, nstart = 10)
print(cluster)

# visualize clusters
fviz_cluster(cluster, mkt1, ellipse.type = "norm", geom = "point")
```


## Visualize Cluster Segements
```{r}
ggplot(mkt1,aes(cluster$cluster))+geom_bar()

ggplot(mkt1,aes(x=age))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=age))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=income))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=income))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=wines))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=wines))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=fruits))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=fruits))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(meat))+geom_bar()
ggplot(mkt1,aes(meat))+geom_bar()+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(fish))+geom_bar()
ggplot(mkt1,aes(fish))+geom_bar()+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(gold))+geom_bar()
ggplot(mkt1,aes(gold))+geom_bar()+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=deals))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=deals))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=cmplain))+geom_histogram(binwidth=1)
ggplot(mkt1,aes(x=cmplain))+geom_histogram(binwidth=1)+facet_wrap(~cluster$cluster)

ggplot(mkt1,aes(x=cluster$cluster))+geom_bar()+facet_wrap(~mkt$response) + labs(title = "Response by Clusters")

ggplot(mkt,aes(response))+geom_bar()+facet_wrap(~cluster$cluster)+geom_text(stat='count', aes(label=..count..), vjust = 1.2, colour = "white")+labs(title = "Response by Clusters")
```


## Data Preparation
```{r}
mktfin <- mkt %>%
  mutate(cmp1 = as.factor(cmp1)) %>%
  mutate(cmp2 = as.factor(cmp2)) %>%
  mutate(cmp3 = as.factor(cmp3)) %>%
  mutate(cmp4 = as.factor(cmp4)) %>%
  mutate(cmp5 = as.factor(cmp5)) %>%
  mutate(education = as.factor(education)) %>%
  mutate(mar_stat = as.factor(mar_stat)) %>%
  mutate(cmplain = as.factor(cmplain)) %>%
  mutate(response = as.factor(response))

skim(mktfin)


new_pred <- new %>%
  mutate(cmp1 = as.factor(cmp1)) %>%
  mutate(cmp2 = as.factor(cmp2)) %>%
  mutate(cmp3 = as.factor(cmp3)) %>%
  mutate(cmp4 = as.factor(cmp4)) %>%
  mutate(cmp5 = as.factor(cmp5)) %>%
  mutate(education = as.factor(education)) %>%
  mutate(mar_stat = as.factor(mar_stat)) %>%
  mutate(cmplain = as.factor(cmplain))

skim(new_pred)
```


## Data Partition
```{r}
set.seed(43)
mkt_split <- initial_split(mktfin, prop = 0.7)
train <- training(mkt_split)
test <- testing(mkt_split)

sprintf("Train PCT : %1.2f%%", nrow(train)/nrow(mktfin) * 100)
sprintf("Test  PCT : %1.2f%%", nrow(test)/nrow(mktfin) * 100)
```


## Recipe - Full Model
```{r}
mkt_recipe <- recipe(response ~ ., data = train) %>%
  step_rm(id, birth, dt_customer) %>%
  step_impute_median(all_numeric()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()

bake_train <- bake(mkt_recipe, new_data = train)
bake_test <- bake(mkt_recipe, new_data = test)
```


## Logistic Regression - Full Model
```{r}
logistic_glm <- logistic_reg(mode = "classification") %>%
  set_engine("glm") %>%
  fit(response ~ ., data = bake_train)

tidy(logistic_glm) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"), round, 4)

logistic_glm %>%
  vi()
```


## Prepare for Full Model Evaluation
```{r}
# -- training 
predict(logistic_glm, bake_train, type = "prob") %>%
  bind_cols(.,predict(logistic_glm, bake_train)) %>%
  bind_cols(.,bake_train) -> scored_train_glm

head(scored_train_glm)

# -- testing 
predict(logistic_glm, bake_test, type = "prob") %>%
  bind_cols(.,predict(logistic_glm, bake_test)) %>%
  bind_cols(.,bake_test) -> scored_test_glm

head(scored_test_glm)
```


## Full Model Evaluation
```{r}
event_level = 'first'

# -- AUC: Train and Test 
scored_train_glm %>% 
  metrics(response, .pred_1, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test_glm %>%
              metrics(response, .pred_1, estimate = .pred_class) %>%
              mutate(part = "testing"))

# -- ROC Charts 
scored_train_glm %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_glm %>%
              mutate(model = "test")) %>%
  group_by(model) %>%
  roc_curve(response, .pred_1) %>%
  autoplot()

# -- Confusion Matrix  
scored_train_glm %>%
  conf_mat(response, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Train Confusion Matrix")

scored_test_glm %>%
  conf_mat(response, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title="Test Confusion Matrix")
```


## Reduce Model (Stepwise)
```{r}
steplog <- glm(response ~ ., data = bake_train, family = binomial(link = "logit"))
step <- stepAIC(steplog, direction = "both")
summary(step)
```


## Step Recipe - Final
```{r}
finalrecipe <- recipe(response ~ teens + recency + meat + deals + web + catalog + store + visits + education + mar_stat + cmp3 + cmp4 + cmp5 + cmp1 + cmp2, data = train) %>%
  step_impute_mode(all_nominal(), -all_outcomes()) %>%
  step_impute_median(all_numeric()) %>%
  step_dummy(all_nominal(), -all_outcomes()) %>%
  prep()

finalrecipe
```


## Apply New Recipe to Final Model
```{r}
bake_finaltrain <- bake(finalrecipe, new_data = train)
bake_finaltest <- bake(finalrecipe, new_data = test)

logis_final <- logistic_reg(mode = "classification") %>%
  set_engine("glm") %>%
  fit(response ~ ., data = bake_finaltrain)

tidy(logis_final) %>%
  mutate_at(c("estimate", "std.error", "statistic", "p.value"), round, 4)
```


## Prepare for Final Evaluation
```{r}
predict(logis_final, bake_train, type = "prob") %>%
  bind_cols(., predict(logis_final, bake_train)) %>%
  bind_cols(., bake_train) -> scored_train_final

head(scored_train_final)


predict(logis_final, bake_test, type = "prob") %>%
  bind_cols(., predict(logis_final, bake_test)) %>%
  bind_cols(., bake_test) -> scored_test_final

head(scored_train_final)
```


## Evaluation for Final Model
```{r, warning=FALSE}
options(yardstick.event_first = FALSE)

# -- evaluation metrics
scored_train_final %>%
  metrics(response, .pred_1, estimate = .pred_class) %>%
  mutate(part = "training") %>%
  bind_rows(scored_test_final %>%
              metrics(response, .pred_1, estimate = .pred_class) %>%
              mutate(part = "testing"))

# -- auc_roc curve
scored_train_final %>%
  mutate(model = "train") %>%
  bind_rows(scored_test_final %>%
              mutate(model = "test")) %>%
  group_by(model) %>%
  roc_curve(response, .pred_1) %>%
  autoplot()

# -- confusion matrix
scored_train_final %>%
  conf_mat(response, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Train Confusion Matrix")

scored_test_final %>%
  conf_mat(response, .pred_class) %>%
  autoplot(type = "heatmap") +
  labs(title = "Test Confusion Matrix")
```


## Apply Model to New Predictions
```{r}
bake_new <- bake(finalrecipe, new_data = new_pred)

scored_new <- predict(logis_final, bake_new, type = "prob") %>%
  bind_cols(., predict(logis_final, bake_new)) %>%
  bind_cols(., new_pred)

scored_new %>% write_csv("new_response.csv")
```

